\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-20 ase20/intro.tex
[ASE] minor changed: ES 5.1 -> ES5.1
[ASE] Revised intro for the new flow

Moreover, JavaScript syntax and semantics are annually updated.  Until
ES 5.1, JavaScript was a stable language because the specification was
rarely updated.  However, the Ecma Technical Committee 39 (TC39)~\cite{tc39}
decided to release the specification annually in late 2014.  After this official
announcement, several syntax features and roughly 1,000 to 3,000 steps of
abstract algorithms have been modified or newly added in the specification every year.
To handle these frequent and massive updates of ECMAScript,
the manual approaches require researchers to manually update parsers and AST-IR translators,
which incurs tremendous efforts.

@@

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that can automatically synthesize}
    parsers and AST-IR translators directly from a language specification,
    ECMAScript.}  For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules due to the
    difficulty in handling the semantics written in a natural language.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the five most recent ECMAScript versions (ES6 to ES10).   \( \tool \) automatically generated
    parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{ Using \( \tool \), we could define the \textit{first IR-based
    formal semantics of modern JavaScript}.}  The semantics targets the
    core of ES10, and \( \tool \) successfully synthesizes its
    parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
    algorithm steps.  We manually completed the missing parts of the AST-IR
    translator (\inred{XXX} steps) in \inred{XX} days.  We evaluated the correctness
    of the formal semantics using Test262~\cite{test262}, the official
    conformance test suite, and the semantics passed all \inred{XX,XXX}
    applicable tests.  Moreover, we found \inred{X} specification errors in ES10
    thanks to the formal semantics.  They were all confirmed by TC39 and will be
    fixed in the next release.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new language features
    proposed for future ECMAScript specifications.}  
     We evaluated the forward compatibility of \( \tool \) by applying it
     to all \inred{XX} proposals that are ready for inclusion in the next ECMAScript  (ES11, 2020).
    It automatically synthesized parsers and
    compiled \inred{XX} out of \inred{XX} algorithm steps for all the proposals.
    After completion of the missing parts, the extracted semantics passed all \inred{XX} tests.
\end{itemize}

>>>>

Moreover, JavaScript syntax and semantics are annually updated.  Until
ES5.1, JavaScript was a stable language because the specification was
rarely updated.  However, the Ecma Technical Committee 39 (TC39)~\cite{tc39}
decided to release the specification annually in late 2014.  After this official
announcement, several syntax features and roughly 1,000 to 3,000 steps of
abstract algorithms have been modified or newly added in the specification every year.
To handle these frequent and massive updates of ECMAScript,
the manual approaches require researchers to manually update parsers and AST-IR translators,
which incurs tremendous efforts.

@@

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges the gap between tests and the specification
    written in a natural language.}
    The formal semantics automatically extracted by \( \tool \) is executable
    and its components have one-to-one correspondences with the components of
    the ECMAScript.  It gives opportunity to directly verify the specification
    through the official test conformance suite, Test262~\cite{test262}.  We
    manually completed the missing parts for the latest ECMAScript (ES10, 2019),
    and it is the \textit{first IR-based formal semantics of modern JavaScript}.
    By executing tests, we found \inred{X} specification errors in ES10 and
    \inred{XX} wrong tests in Test262. They were all confirmed by TC39 and will
    be fixed in the next release.  After fixing them, our formal semantics
    passed all \inred{XX,XXX} applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}
